site_map

### 2020-01-17 site_map.Rmd
update

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  # site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixel <- transect.pixel(site, c(10000, 30000, 50000))
  site_pixels <- rbind(site_pixels, site_pixel)
}

# New site pixels
save(site_pixels, file = "Data/site_pixels_new.RData")
load("Data/site_pixels_new.RData")
# save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")

@@

load("Data/south_africa_coast.RData")
load("Data/africa_coast.RData")
load("Data/sa_provinces_new.RData")
load("Data/site_list_sub.Rdata")
load("Data/site_pixels_new.RData")
# load("Data/site_pixels.RData")
load("MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + bw_update +
  # geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 5) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub_map, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = -0.5, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(12, 23), ylim = c(-36,-26), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 17.00, y = -35.0,
             size =6, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 14.0, y = -29.5,
             size = 6, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5),
        axis.text = element_text(size = 12)) +
    guides(fill = guide_colourbar(barheight = 1.00, barwidth = 10)) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.minor = element_line(colour = "NA"),
        panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
        legend.direction = "horizontal",
        legend.justification = c(1,0),
        legend.position = c(0.85, 0.70),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5))
site_map

>>>>

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  #site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
  site_pixel <- transect.pixel(site, c(10000, 30000, 50000))
  site_pixels <- rbind(site_pixels, site_pixel)
}

# New site pixels
# save(site_pixels, file = "Data/site_pixels_new.RData")
# load("Data/site_pixels_new.RData")
# save(site_pixels, file = "Data/site_pixels.RData")
 load("Data/site_pixels.RData")

@@

load("Data/south_africa_coast.RData")
load("Data/africa_coast.RData")
load("Data/sa_provinces_new.RData")
load("Data/site_list_sub.Rdata")
load("Data/site_pixels_new.RData")

#load("Data/site_pixels.RData")
load("MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  # geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 5) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub_map, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(12, 23), ylim = c(-36,-26), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 17.00, y = -35.0,
             size =6, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 14.0, y = -29.5,
             size = 6, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5),
        axis.text = element_text(size = 12)) +
    guides(fill = guide_colourbar(barheight = 1.00, barwidth = 10)) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.minor = element_line(colour = "NA"),
        panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
        legend.direction = "horizontal",
        legend.justification = c(1,0),
        legend.position = c(0.85, 0.70),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5))
site_map
